---
title: "Test"
author: "Philipp Penner"
date: "25 10 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

```{r warning=FALSE}
# install.packages("imgrec")
library(imgrec)
library(tidyverse)
library(quanteda)
```

```{r}
# store & hide GCV API key in .Renviron file
#usethis::edit_r_environ()
```

```{r}
# API key set as environment variable
Sys.setenv(gvision_key = Sys.getenv('GCV_key'))
```

```{r}
# initialization function 
gvision_init()
```

# get image annotations
# each for women and men
```{r}
# get list of paths to the images
filenames_woman <- list.files(path = "mc_images_split/mc_woman", 
                        pattern="*.jpg", 
                        full.names = TRUE)
head(filenames_woman)
```

```{r}
# get list of paths to the images
filenames_men <- list.files(path = "mc_images_split/mc_men", 
                        pattern="*.jpg", 
                        full.names = TRUE)
head(filenames_men)
```

```{r}
results_woman <- get_annotations(images = filenames_woman,  # image character vector
                           features = 'label',              # request all available features
                           max_res = 25,                    # maximum number of results per feature
                           mode = 'local')                  # determine image type

img_data_woman <- parse_annotations(results_woman) # returns list of data frames
names(img_data_woman) # all available features
```

```{r}
results_men <- get_annotations(images = filenames_men,      # image character vector
                           features = 'label',              # request all available features
                           max_res = 25,                    # maximum number of results per feature
                           mode = 'local')                  # determine image type

img_data_men <- parse_annotations(results_men) # returns list of data frames
names(img_data_men) # all available features
```

# get labels
```{r}
img_labels_woman <- img_data_woman$labels
head(img_labels_woman)
```

```{r}
img_labels_men <- img_data_men$labels
head(img_labels_men)
```

```{r}
# save data
write.csv(img_labels_woman, 
          file = "data_replication/imgrec_women_18.01.23.csv", 
          row.names = F)
```

```{r}
# save data
write.csv(img_labels_men, 
          file = "data_replication/imgrec_men_18.01.23.csv", 
          row.names = F)
```

# import
```{r}
library(readr)
df_woman <- read_csv("data_replication/imgrec_woman_28.12.22.csv")
df_men   <- read_csv("data_replication/imgrec_men_28.12.22.csv")
```

```{r}
head(df_woman)
df_woman <- aggregate(description ~ img_id, data = df_woman, FUN = c)
df_woman <- df_woman %>% add_column(gender = "Female", .before = "description")
```

```{r}
head(df_men)
#df_men <- aggregate(description ~ img_id, data = df_men, FUN = c)
df_men <- df_men %>% add_column(gender = "Male", .before = "description")
```

```{r}
df_total <- full_join(df_woman, df_men)
dim(df_total)
```


```{r}
# recode description
df_total$description <- sapply(df_total$description, paste, collapse = ", ")
```


## Image labels - key differences

Next, we quantify key differences in labels by gender for each image recognition service. We only consider labels that were assigned at least 5 times across all images.

```{r}
gcv_dfm <- corpus(df_total,
                  text_field = 'description',
                  docid_field = 'img_id') %>%
  dfm(remove_punct = TRUE) %>% 
  dfm_trim(min_termfreq = 5)

dim(gcv_dfm)
```


We create a function to examine group differences based on Chi² tests. 
Get 25 most gendered labels

Todo: Wie funktioniert diese Funktion genau???

```{r}
key_diff <- function(featmat, groups, 
                     groups1_name,
                     groups2_name,
                     group1_obs, group2_obs) {
  # grouping
  img_grouped <- dfm_group(featmat, groups = groups)
  
  
  # compute key labels for group 1
  key1 <- textstat_keyness(img_grouped,  target = groups1_name, measure = 'chi2')
  group_key1 <-
  key1 %>% mutate(
    groups = if_else(chi2 >= 0, groups1_name, groups2_name),
    key = groups1_name,
    chi2_abs = abs(chi2),
    obs_total = group1_obs
  ) %>%
  group_by(groups) %>% top_n(n = 25, wt = chi2_abs) %>% ungroup()

  # compute key labels for group 2
  key2 <- textstat_keyness(img_grouped,  target = groups2_name, measure = 'chi2')
  group_key2 <-
  key2 %>% mutate(
    groups = if_else(chi2 >= 0, groups2_name, groups1_name),
    key = groups2_name,
    chi2_abs = abs(chi2),
    obs_total = group2_obs
  ) %>%
  group_by(groups) %>% top_n(n = 25, wt = chi2_abs) %>% ungroup()
  
  
  # combine data and add frequency indicators
comb_key <- group_key1 %>% bind_rows(group_key2) %>%
  mutate(sum_feat = n_target + n_reference,
    rel_feat =  n_target / sum_feat,
    rel_total =  n_target / obs_total,
    feature = str_replace_all(feature, '_', ' ') %>% 
              str_trim() %>% 
              reorder_within(sum_feat, groups))

return(comb_key)

}
```


### GCV

Figure with top labels of woman/man

```{r fig.height=6, fig.width=8}
# apply function
gcv_diff <- key_diff(gcv_dfm, groups = "gender", groups1_name = "Female",
         groups2_name = "Male", group1_obs = 110, group2_obs = 430)

# visualize results
gcv_diff_plot <- gcv_diff %>%
  ggplot(aes(x = feature, rel_total, fill = key)) +
  geom_bar(stat = "identity", position = "dodge")  +
  coord_flip() +
  facet_wrap(ifelse(groups == "Male", "Top labels,\nimages of men",
                    "Top labels,\nimages of women") ~ .,
              scales = 'free_y')  +
  
  scale_x_reordered() +
  scale_y_continuous(labels = scales::label_percent(suffix = ""),
                     breaks = pretty_breaks(n = 5)) +
  
  scale_fill_manual(
    values = viridis(n = 4)[c(1, 3)],
    name = "% receiving each label",
    labels = c("Women", "Men")
  )  +
  labs(x = '',
       y = '') + 
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.box.background = element_rect(colour = "grey80"),
    legend.text = element_text(size = 10),
    axis.text.x = element_text(angle = 0),
    axis.text.y = element_text(size = 10),
    strip.text.x = element_text(size = 12),
    axis.title.y = element_blank())

gcv_diff_plot

ggsave(
 'figures/fig6_replication.png',
 gcv_diff_plot,
 dpi = 300,
 width = 8,
 height = 6
)
```



# wordcloud
```{r}
#install.packages("wordcloud")
#install.packages("tm")
#install.packages("RColorBrewer")
library(wordcloud)
library(tm)
library(RColorBrewer)
```

# prepare data
```{r}
dtm <- TermDocumentMatrix(df_men$description)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)

head(d, 20)
```

# create wordcloud
```{r}
set.seed(42)

wordcloud(words = d$word, 
          freq = d$freq, 
          min.freq = 1,
          max.words = 200, 
          random.order = FALSE, 
          rot.per = 0.6, 
          colors = brewer.pal(8, "Spectral"))
```






















































